---
title: "Traveling Professor Problem"
author: "Carlos Pelayo"
date: "4/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSP)
```
## The Problem
Young Field Baker is planning his trip to CSUB campus.  He must make 5 stops and one visit to a restroom.  He starts and ends the day at the bus stop on campus

The stops he must make and the North, East coordinates of each are givnen in the following table: (units are Cubits)

   Location     |  coordinates (N, W)
   -------------|--------------------
   Bus stop     |  25, 200
   Engineering Complex |  110, 160
   Dorthy Donahue Building  |  250, 200
   Student Union  |  250, 300
   Walter Stern Library  | 300, 250
   Administration Building | 260  , 50
   
   In addition he must one stop at a  restroom; the available restrooms are at locations (200,160), (340,110), and (280,290)
   
   Find the shortest route freshman Field can take on this visit.  Only 1 restroom stop
   
## Set up data 
```{r}
n1=c(25,110,250,250,300,260,200)
w1=c(200,160,200,300,250,50,160)
n2=c(25,110,250,250,300,260,340)
w2=c(200,160,200,300,250,50,110)
n3=c(25,110,250,250,300,260,280)
w3=c(200,160,200,300,250,50,290)
x=c("Bus Stop","Engineering Complex","Dorthy Donahue","Student Union","Library","Admin Building","Bath")

p1=ETSP(data.frame(n1,w1),labels=x)
p2=ETSP(data.frame(n2,w2),labels=x)
p3=ETSP(data.frame(n3,w3),labels=x)

```
## First Set Solution
```{r}
## calculate a tour
p1
tour1 <- solve_TSP(p1)
tour_length(tour1)
plot( p1,tour1,tour_col = "red")
text(p1,labels = x,cex=0.75)

```
## Second Set Solution
```{r}
## calculate a tour
tour2 <- solve_TSP(p2)
tour_length(tour2)
plot( p2,tour2,tour_col="blue")
text(p2,labels = x,cex=0.75)
```  
 
## Third Set Solution
```{r}
## calculate a tour
tour3 <- solve_TSP(p3)
tour_length(tour3)
plot( p3,tour3,tour_col="green")
text(p3,labels = x,cex=0.75)
```

## Solution
   The shortest route possible is 823.561 cubits long. The path that would need to be taken is from the $Bus Stop$ to the $Engineering Complex$ then the $Administration Building$ then the $Dorthy Donahue$ building then the $Library$ then the $Third Bathroom$ followed by the  $Student Union$ and then returning to the $Bus Stop$. 